State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.5~\%). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian. The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.

\begin{table}
\centering
\begin{tabular}{cccc}
	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Standard Deviation \\
	\hline\hline
 	$\xi$ & 0.9 & 0.925 $\pm$ 0.004 \\
	$\theta_0$ & 10 & 10.295 $\pm$ 2.879 \\
	$\theta_1$ & -8 & -8.571 $\pm$ 1.996 \\
	$\theta_2$ & 0.5 & 0.551 $\pm$ 0.083 \\
\end{tabular}
\caption{Actual parameter values and mean parameter estimates and standard deviation.}
\label{tab:Parameters estimates}
\end{table}

>>>>

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.778~\%). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian. The mean parameter estimates are in good accordance with the actual values, with biases of 2.95, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.

\begin{table}
\centering
\begin{tabular}{cccc}
	\hline\hline Parameter & Actual Value & Mean Estimate $\pm$ Standard Deviation \\
	\hline\hline
 	$\xi$ & $0.9$ & $0.925\pm 0.004$ \\
	$\theta_0$ & $10$ & $10.295\pm2.879$\\
	$\theta_1$ & $-8$ & $-8.571\pm1.996$ \\
	$\theta_2$ & $0.5$ & $0.551\pm0.083$ \\
\hline\hline
\end{tabular}
\caption{Actual parameter values and parameter estimates. Plus-minus figures are mean $\pm$ standard deviation.}
\label{tab:Parameters estimates}
\end{table}
